The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2006-01-04 trunk/vcd/paper/JSS.Rnw
strucplot framework update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@505 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

So far, we have visualized full tables. For objects of class \class{table},
conditioning on levels (i.e., choosing a table subset for fixed levels
of the conditioning variable(s)) is simply done by indexing.
However, subsetting \class{structable} objects is more restrictive 
because of their inherent conditional structure. Since the variables
on both the row and the columns side are nested, 
conditioning is only possible ``outside-in'':

<<subsetting,results=verbatim>>=
hec
hec["Male",]
hec[c("Male", "Brown"),]
hec["Male","Green"]
@

@@

pushViewport(viewport(layout.pos.col = 1))
mosaic(hec["Male"], margins = c(left = 2.5, top = 2.5, 0), sub = "Male", newpage = FALSE)
popViewport()

pushViewport(viewport(layout.pos.col = 2))
mosaic(hec["Female"], margins = c(top = 2.5, 0), sub = "Female", newpage = FALSE)
popViewport(2)
@

>>>>

So far, we have visualized full tables. Subtables can be selected in a
similar way than for objects of class \class{table} using
indexing. Note, however, that subsetting of \class{structable} objects 
is more restrictive because of their inherent conditional structure. Since the variables
on both the row and the columns side are nested, 
subsetting is only possible ``outside-in'', that is, indexing operates
on blocks defined by the variable levels:

<<subsetting,results=verbatim>>=
hec
hec["Male",]
hec["Male", c("Brown","Green")]
@

\noindent \emph{Conditioning} on levels (i.e., choosing a table subset for fixed levels
of the conditioning variable(s)) is done using the \code{[[} operator. %]]
Here again, the sequence of conditioning levels is restricted by the
hierarchical structure of the \class{structable} object:

<<conditioning,results=verbatim>>=
hec[["Male",]]
hec[[c("Male", "Red"),]]
hec[["Male","Green"]]
@

@@

pushViewport(viewport(layout.pos.col = 1))
mosaic(hec[["Male"]], margins = c(left = 2.5, top = 2.5, 0), sub = "Male", newpage = FALSE)
popViewport()

pushViewport(viewport(layout.pos.col = 2))
mosaic(hec[["Female"]], margins = c(top = 2.5, 0), sub = "Female", newpage = FALSE)
popViewport(2)
@
